\subsection{Natural aerosol emissions in Australia}
Natural emissions in Australia are important due to the large population sparse areas from where dust, isoprene, and other important aerosols are released.
The Australian outback is described by extremely large and diverse environments, mixed with a dearth of in-situ measurements this leads to uncertainty in estimates of aerosol densities and distributions.

One source of information which covers the entirety of Australia is remote sensing performed from satellites which overpass daily and record reflected solar spectra.
These can be used to garner details of several chemicals as well as estimates of their distribution in vertical columns over the land.
While satellite data is very good for covering huge areas (the entire earth) it only exists at a particular time of day, is subject to cloud cover, and generally does not have fine horizontal or vertical resolution.
A problem with the vertical profiles from satellites is that they are estimates based on forward radiative transfer modelling.
This leaves us with a best guess for chemical concentrations at any altitude which may need verification or adjustment.

Several satellites provide long term trace gas data with near complete global coverage, including GOME (1, 2 metop A, and 2 metop B), OMI AURA, and SCIAMACHY.
These satellites are on Low Earth Orbit (LEO) trajectories and overpass any area up to once per day. 
They record near nadir reflected spectra between around 250-700~nm split into spectral components at around $0.3$~nm in order to calculate trace gases including O$_3$, NO$_2$, BrO, SO$_2$, and HCHO.


\subsection{Chemical Transport Models (CTMs)}
CTMs simulate production, loss, transport, and deposition of chemical species.
Generally CTMs will solve the continuity equations numerically for chemicals under inspection using one or both of the Eulerian (box) or Lagrangian (puff) frames of reference.
Where measurements exist they can be fed into CTMs as boundary and/or initial conditions in order to both examine real world concentrations and limit model uncertainty and divergence.
GEOS-Chem is the CTM which I am interested in and is a 3-D global CTM for atmospheric composition with transport driven by meteorological input from the Goddard Earth Observing System (GEOS) of the NASA Global Modeling and Assimilation Office (GMAO).
GEOS-Chem simulates more than 100 chemical species from the earth's surface up to the top of the atmosphere and can be used in combination with remote and in-situ sensing data to give a confident estimate of elements in remote areas.

Combining satellite and modelled data could allow for improved accuracy in records of natural Australian chemical sources as well as allow analysis of past and potential impacts of climate and environmental changes.
Due to the low availability of in-situ data covering most of the Australian outback an analysis of the modelled and remote sensed data could provide improved accuracy for global records of emissions which would in turn improve the accuracy or confidence of many models which are constrained or driven by these global inventories.


\subsection{Dust, aerosols, and climate}
\begin{quote}
Aerosols partially offset the forcing of the WMGHGs and dominate the uncertainty associated with the total anthropogenic driving of climate change \cite{IPCC_2013_chap8}.
\end{quote}

The Australian dust story is one of extremes, convolving the ENSO cycle with flooding, droughts, and winds.
Fluvial deposits in the Eyre basin are required to provide a dust base, which will only have mobility during suitable dry weather conditions, which are saltated and transported by strong winds\cite{Zender_2003}.

Australia is the largest source of dust in the southern hemisphere producing around 120~Tg$a^{-1}$ \cite{Li_2008}, however model validation and analysis over Australia is relatively scarce with more focus applied to the northern hemisphere.
Aeolian dust has many direct effects including reduced surface insolation, mineral transfer to remote ocean regions, and health degradation in populated areas.
Direct and indirect effects of dust have many implications which are not fully understood, with many models still struggling to explain the role of dust at larger scales \cite{Rotstayn_2011}.

Synoptic scale measurements of dust plumes in Australia are kept by the BoM and can be used to estimate dust transport caused by large storms(\cite{Leys_2011}, todo more cites here). 
These estimates exemplify the large variability in Australian annual dust transport with single storms moving up to 2.5 Mt of dust off shore in a single day, with impacts on population health, oceanic carbon production, and erosion cycles \cite{Leys_2011,Shao_2007}.

\subsubsection{Oceanic Deposition}
Oceanic carbon cycling is a complex system in which iron (Fe) is a limiting factor, required by diazotrophs in order to fix atmospheric Nitrogen into a more bioavailable form such as ammonia.
Atmospheric deposition into the oceans is a very poorly constrained variable in global models (\cite{Grand_2015} more CITES).
Various estimates of trace element oceanic depositions are required due to a dearth of in situ measurements in remote open ocean regions.

Measurements of dissolved iron (DFe) at very low concentrations like those found in surface ocean waters are very easily contaminated, which has contributed the the fragmentary and scarce nature of DFe ocean data sets \cite{Rijkenberg_2014}.
Recent analysis of the US Climate Variability and Predictability (CLIVAR)-CO$_{2}$ Repeat Hydrography Program predicted total deposition flux with uncertainty at a factor of 3.5 due mostly to assumed Aluminium solubility and residence time \cite{Grand_2015}.
Some headway has been made with the recent GEOTRACES program which has several transects of the major oceans and measures trace elements over multiple depths including Al, Ba, Cu, Cd, Fe, Mn, Ni, Pb, and Zn.
  
Total iron (TFe) emissions from dust and combustion sources are estimated (by average of several global models) at approximately 35~Tg yr$^{-1}$ and 2Tg yr$^{-1}$ respectively. A three fold increase in Fe dissolution may have occurred since 1850 due to increased anthropogenic emissions and atmospheric acidity, with a 30\% decrease projected from current levels by 2100 \cite{Myriokefalitakis_2015}.
Dust, TFe and DFe have strong temporally and spatial variability, with changes having most impact upon high nutrient low chlorophyll (HNLC) regions.

  
  
  