\section{Preliminary Literature Review}
\subsection{Dust Summary}
\begin{quote}
Aerosols partially offset the forcing of the WMGHGs and dominate the uncertainty associated with the total anthropogenic driving of climate change.
\end{quote} \cite{IPCC_2013_chap8}.
\subsubsection{Australia}

The Australian dust story is one of extremes, convolving the ENSO cycle with flooding, droughts, and winds.
Fluvial deposits in the Eyre basin are required to provide a dust base, which will only have mobility during suitable dry weather conditions, which are saltated and transported by strong winds(\cite{Zender_2003}).

Australia is the largest source of dust in the southern hemisphere, however model validation and analysis over Australia is relatively scarce with more focus applied to the northern hemisphere.
Aeolian dust has many direct effects including reduced surface insolation, mineral transfer to remote ocean regions, and health degradation in populated areas.
Direct and indirect effects of dust have many implications which are not fully understood, with many models still struggling to explain the role of dust at larger scales \cite{Rotstayn_2011}.

Synoptic scale measurements of dust plumes in Australia are kept by the BoM and can be used to estimate dust transport caused by large storms(\cite{Leys_2011}, todo more cites here). 
These estimates exemplify the large variability in Australian annual dust transport with single storms moving up to 2.5 Mt of dust off shore in a single day, a significant portion of the yearly mean dust removal \cite{Leys_2011,Shao_2007}.

\subsubsection{Oceanic Deposition}
Oceanic carbon cycling is a complex system in which iron is a limiting factor, required by diazotrophs in order to fix atmospheric Nitrogen into a more bioavailable form such as ammonia.
Atmospheric deposition into the oceans is a very poorly constrained variable in global models (\cite{Grand_2015} more CITES).
Various estimates of trace element oceanic depositions are required due to a dearth of in situ measurements in remote open ocean regions.

Measurements of dissolved iron (DFe) at very low concentrations like those found in surface ocean waters are very easily contaminated, which has contributed the the fragmentary and scarce nature of DFe ocean data sets \cite{Rijkenberg_2014}.
Recent analysis of the US Climate Variability and Predictability (CLIVAR)-CO$_{2}$ Repeat Hydrography Program predicted total deposition flux with uncertainty at a factor of 3.5 due mostly to assumed Aluminium solubility and residence time \cite{Grand_2015}.
Some headway has been made with the recent GEOTRACES program which has several transects of the major oceans and measures trace elements over multiple depths including Al, Ba, Cu, Cd, Fe, Mn, Ni, Pb, and Zn.
  
  
  
  
  
  
  
  
  