\section{Dust}

\subsection{McTainsh 2005}
4.2 Mt dust load estimated for October 2002 dust storm.

\subsection{ENSO dust \cite{Rotstayn_2011}}
Simulated enhancement of NESO-related rainfall variability due to Australian dust

CSIRO Mark 3.6 GCM is run for 160 years twice, with and without the mineral dust source in Australia set to zero.
ENSO related rainfall variability improves over eastern Australia relative to observations.

An indirect effect of Dust is the stabilisation of the lower troposphere, where reduced insolation at the surface somewhat flattens the temperature gradient in the lower troposphere.

\subsection{Red Dawn: \cite{Leys_2011}}
PM10 concentrations and mass transport during "Red Dawn" - Sydney 23 September 2009.

Worst dust storm to hit Sydney since records began in 1940, with heavy dust for nine hours and visibility reduced to 400m at the airport.
Storms are common in the arid inland but rare on the east coast.
Plume dust concentration generally calculated either by simulation, or by plume volume * aerosol concentration.
$$M = AhC$$ 
where A is plume area, h is plume height, C is g/m3 of dust, M is dust load in grams.
These measurements are hampered by coarse temporal resolution of at best three hourly intervals of the Bureau of Meteorology(BoM)'s synoptic visibility observations.

Dust concentrations sourced from some stations of the DECCW AQMN.

Visibility is used to estimate total suspended particle(TSP) concentration, here a conservative predictor of PM10 c for given V is used from (Zhangbei TODO CITE).

PM10 dust transport is defined and measured with plume dust concentrations measured at various altitudes with a kite. 

Dust storm preceded by 9 dry years, 13 hot years, and was itself the hottest year on record.

PM10 normally $10{\mu}g/m^3$ in Sydney peaked at $15366{\mu}g/m^3$.
\~2.54 Mt of PM10 dust transported off shore.
Storm on par with large Chinese dust storm.
Dust ceiling around 2500m, up to 3000m.

\subsection{Atlantic Ocean Deposition \cite{Rijkenberg_2014}}
The Distribution of Dissolved Iron in the West Atlantic Ocean.

\begin{quote}
Highly accurate dissolved Fe (DFe) values measured at an unprecedented high intensity (1407 samples) along the longest full ocean depth transect (17500 kilometers) covering the entire western Atlantic Ocean.
\end{quote}

\begin{quote}
Vertical processes such as the recycling of Fe resulting from the remineralization of sinking organic matter and the removal of Fe by scavenging still dominated the distribution of DFe. In the northern West Atlantic Ocean, Fe recycling and lateral transport from the eastern tropical North Atlantic Oxygen Minimum Zone (OMZ) dominated the DFe-distribution.
\end{quote}

\subsection{Indian Ocean Deposition Measurements \cite{Heimburger_2013}}
Samples from Kerguelen and Crozet islands January - November 2010, compared against SLRS-4 and SLRS-5

Daily Fe deposition at three sites over the two islands in ${\mu}gm^{-2}d^{-1} \pm SD$:
29.1 $\pm$ 1.3, 38.7 $\pm$ 4.1, 34.6 $\pm$ 2.1

Typically three methods are used to estimate oceanic deposition: a) land based extrapolation, b) shipboard aerosol measurements, and c) surface water measurements. 
These methods each have their own problems, and all suffer from high uncertainties. 
A fourth method using Aerosol Optical Depth(AOD) recorded by satellites in combination with estimated Fine Mode Fraction(FMF), wind, and precipitation data allows remote ocean deposition estimates but this method lacks good verification(again due to lack of in situ measurements). 

\subsection{Atlantic Deposition Gregory R. Foltsz 2014 Conference}
Satellite and in situ estimates of dust deposition in the tropical North Atlantic.

Fine Mode Fraction, AOD from Terra MODIS satellite, winds from NCEP/NCAR reanalysis, precipitation from TRMM satellite are all used together to estimate oceanic wet and dry deposition.
Shortwave surface radiation biases from dust accumulation allow independent dry deposition measurements for comparison.

Using modified Kaufman 2005 methodology to calculate deposition and comparing against PIRATA moorings data which allows estimates of dry deposition based on dust accumulation biases in surface shortwave radiation records.

\subsection{Dissolved Iron in West Atlantic \cite{Rijkenberg_2014}}
Iron is an essential trace element for marine life.
Low iron concentrations limit primary production and nitrogen fixation.
Fe strongly correlated with Aluminium and Mangenese in surface waters.

Measurements of low concentrations of dissolved iron are easily contaminated, which makes the measurements relatively rare and fragmentary.

Scavenging of Fe is the primary oceanic removal mechanism. 
Fe-binding ligands may play a role in DFe retention in surface waters, and organic complexation of Fe may help determine DFe distribution.

Main surface oceanic Fe contributions: aeolian dust, river input(26e9~mol y$^{-1}$), hydrothermal vents(3\%).

Attribution is based on concentrations of salinity, aluminium, and iron. 
High DFe with low salinity implies river source, 

\subsection{Indian Ocean Deposition \cite{Grand_2015}}
Dust deposition in the eastern Indian Ocean: The ocean perspective from Antarctica to the Bay of Bengal.

Upper ocean distribution of dissolved Fe and Al in the eastern Indian ocean along a $95^{\circ}$E meridional transect.
Using dissolved Al measured from the CLIVAR-CO$_{2}$ program is used with a simple steady state model to produce estimates of total dust deposition. This assumes many things including that the surface water concentrations of elements are in a steady state to balance out scavenging, which allows the estimate of deposition required to maintain the steady state.

Assuming Al solubility based on latitude (mean at 3.6\%, varies from 0.1 to 49.6\%), with residence time of 5 yrs(elsewhere from 0.5 to 15 yrs), this paper uses a modified version of the Measurement of Al for Dust Calculation in Oceanic Waters(MADCOW).

Conclusion that dust deposition is not the dominant annual source of dFe in the Indian sector of the Southern Ocean, upwelling and deep mixing inputs likely are.
Does not rule out dust importance in short terms(during storms etc).

Some Results:
Minimum dust flux at Southern Ocean : 66$\pm$60 mg m$^{-2}$ yr$^{-1}$, 
Maximums for south Indian subtropical gyre: 940 mg m$^{-2}$ yr$^{-1}$ (at 18S),
southern Bay of Bengal: 2500$\pm$570 mg m$^{-2}$ yr$^{-1}$.

Annual dust deposition in the Southern ocean at around 90$^{\circ}$E is estimated to be around 7\% of the annual mean, Australian dust is mostly deposited east of 90$^{\circ}$E.
  
  